Proposed Solution

### 2017-01-24 CAV17/secs/arch.tex
stuff

\begin{figure*}[tbp] \centering
\includegraphics[width=0.84\textwidth]{figs/overview}
\caption{\app's workflow. The green components represent configuration 
  files, including both training set of configuration files and users' input
  configuration files to verify.
  The blue dashed box is \app. 
  The yellow components are key modules of \app.
  The purple circle is a checker for checking whether the target
  configuration file violates any rule.}
\label{fig-overview}
\end{figure*}

We propose \app, an automatic verification framework for 
software configuration files.
As shown in Sec.~\ref{sec-motiv}, \app can detect many sophisticated 
configuration errors, including ordering errors, missing entry errors,
type errors and integer correlation errors. 
Figure~\ref{fig-overview} shows
a typical \app verification workflow with three steps:
translation, learning, and rule refinement. This section briefly
describes how each step works.

\para{Initial phase}
We start with the assumption 
that we are given a number of (not necessarily correct) 
configuration files, called {\em training set}, 
belonging to the same system, such as MySQL or Apache. 
These files, therefore, follow similar patterns.
%In the following steps,
%we will exploit in a collection of learning algorithms 
%to build rules that describe a language model for the files.

\para{Translator}
The translator module first parses the input training  
set of configuration files, and then transforms them into 
a more structured and typed intermediate representation.
When we infer the types of entries in a configuration file, 
the type of an entry cannot always be fully determined from 
a single value, since it is difficult to understand
the purposes of key-value entries in modern
software configuration files~\cite{xu15hey}.
We address this problem 
by introducing {\em probabilistic types}.
Rather than giving a variable a single type, 
we assign several types over a probability distribution. 
We can later use these well-structured files
as a ``true'' training set to learn the rules.

\para{Learning}
The learner reads a set of configuration  files that have been translated
into well-structured representations. 
The learner employs a learning algorithm, {\em rule association 
algorithm}, to generate various rules,
potentially used to handle different types of configuration errors,
including ordering errors, missing entry errors,
type errors and integer correlation errors.
These rules are the outputs of the learner, 
and will be used to detect errors later.
Because the translator gives the learner probabilistically typed entries,
the learner is also responsible for determining types for these entries.

>>>>

\begin{figure*}[tbp] \centering
\includegraphics[width=0.99\textwidth]{figs/overview}
\caption{\app's workflow.
  The dashed box is the specification learning module. 
  The yellow components are key modules of \app.}
\label{fig-overview}
\end{figure*}

Figure~\ref{fig-overview} gives an overview of the \app framework.
The biggest part is dedicated to 
learning and inferring the specification for configuration 
files. This process is done offline, before the user even starts 
to use \app. There are three main steps in the process:
translation, learning, and rule refinement.

\para{Initial phase}
Since there is no proper formal specification for configuration 
files, we learn the specification from a large number of 
(not necessarily correct) configuration files belonging to the same 
system, such as MySQL or Apache. These files are our training set.

%In the following steps,
%we will exploit in a collection of learning algorithms 
%to build rules that describe a language model for the files.

\para{Translator}
The translator module first parses the input training  
set of configuration files, and then transforms them into 
a more structured and typed intermediate representation.
Most of entries in a configuration file follow a key-value pattern, 
where some environmental variable (``key'') is assigned  a value.
Looking at a single entry, by inspecting the value
we cannot always fully determine the type of the key~\cite{xu15hey}.
We address this problem 
by introducing {\em probabilistic types}.
Rather than giving a variable a single type, 
we assign several types over a probability distribution.

\para{Learning}
The learner reads a set of configuration files that have been translated
into well-structured representations. 
It employs a learning algorithm, {\em rule association 
algorithm}, to generate a list of rules, describing properties 
of configuration files. In a nutshell, the learning algorithm 
takes a set of rule interfaces and instantiate them with the concrete
values that appear in the training set. Since there are no guarantees 
that the files in the training set are correct, our main assumption
is that even if a file contains an error, majority of the files do not 
have the same error and our learning process should detect these

generate concrete instances of t

\ruzica{i need to read the rest of the paper first}

These rules are the outputs of the learner, 
and will be used to detect errors later.
Because the translator gives the learner probabilistically typed entries,
the learner is also responsible for determining types for these entries.
